---
title: "Maybe not Simple document"
output: 
  html_document:
    toc: true
---

I'm an R Markdown document! 
# Section 0

```{r, echo= F, message = F}
library(tidyverse)
```

eval: run or not(only code)
echo: show or not(only results)
message: show message while running

# Section 1

Here's a **code chunk** that samples from 
a _normal distribution_:

```{r}
samp = rnorm(100)#this samples from a normal distribution
length(samp)
```

# Section 2

I can take the mean of the sample, too!
The mean is `r mean(samp)`.


# Section 3: a tibble

```{r}
plot_df = 
  tibble(
    x = rnorm(1000,sd = 0.5),
    y = 1 + 2 * x + rnorm(1000) 
  )

head(plot_df, 4)
tail(plot_df, 4)
```

# Section 4
This plot shows the distribution of the abs value of  $X \sim N(500,1,1)

```{r}
ggplot(plot_df, aes(x=x, y = y)) + geom_point()
```

# Section 5
Write a named code chunk that creates a dataframe comprised of: a numeric variable containing a random sample of size 500 from a normal variable with mean 1; a logical vector indicating whether each sampled value is greater than zero; and a numeric vector containing the absolute value of each element. Then, produce a histogram of the absolute value variable just created. Add an inline summary giving the median value rounded to two decimal places. What happens if you set eval = FALSE to the code chunk? What about echo = FALSE

```{r}
la_df = tibble(
  num_var = rnorm(500, mean=1),
  log_var = num_var > 0,
  abs_var = abs(num_var),
) 
ggplot(la_df, aes(x=abs_var))+geom_histogram()+geom_vline(xintercept = mean(la_df$abs_var),color="red",linetype = "dashed")+geom_vline(xintercept = median(la_df$abs_var),linetype = "dotted")
```

The median is `r round(median(pull(la_df, num_var)),2)`.

# Section 6 Text Formatting

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~
Headings

------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header


Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell


# Section 7: Learning Assessment 3

After the previous code chunk, write a bullet list given the mean, median, and standard deviation of the original random sample.





